Supplementary Material for 'New insights into the Weddell Sea ecosystem applying

### 2023-11-06 Manuscript/Manuscript.Rmd
Updated Table 1 main manuscript and tables Supp Material

```{=tex}
\begin{table}[t]
\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p-value). References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p-value.}
\begin{tabular}{l c c c c c c c}
\tophline

\textbf{Species} & \textbf{meanIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} & \textbf{ADvalue}\\
\middlehline
Orcinus orca & 1.83e-4 & 5.03 & 26 & 0.037 & Benthopelagic & 4.67e-5 & 2.28e-41 \\
\middlehline
Macrourus holotrachys & 8.30e-5 & 4.70 & 85 & 0.112 & Benthopelagic & 3.55e-5 & 2.73e-23 \\
\middlehline
Pagetopsis macropterus & 7.08e-5 & 4.64 & 76 & 0.113 & Demersal & -1.80e-5 & 2.38e-12 \\
\middlehline
Abyssorchomene nodimanus & 2.56e-5 & 4.21 & 137 & 0.130 & Benthopelagic & 2.30e-5 & 8.52e-10 \\
\middlehline
Dissostichus mawsoni & 7.82e-5 & 4.12 & 87 & 0.126 & Pelagic & 2.17e-5 & 1.57e-9 \\
\middlehline
Macrourus whitsoni & 7.14e-5 & 4.55 & 92 & 0.124 & Benthopelagic & 2.12e-5 & 3.30e-8 \\
\middlehline
Hydrurga leptonyx & 1.03e-4 & 4.72 & 67 & 0.094 & Land-based & 2.04e-5 & 9.66e-6 \\
\middlehline
Mesonychoteuthis hamiltoni & 1.80e-4 & 4.41 & 29 & 0.028 & Pelagic & 1.82e-5 & 4.59e-5 \\
\middlehline
Champsocephalus gunnari & 7.62e-5 & 3.72 & 46 & 0.086 & Pelagic & 1.83e-5 & 6.79e-5 \\
\middlehline
Notothenia marmorata & 8.27e-5 & 4.09 & 44 & 0.091 & Demersal & 1.60e-5 & 1.23e-4 \\
\middlehline
Arctocephalus gazella & 9.28e-5 & 4.67 & 61 & 0.093 & Land-based & 1.17e-5 & 2.09e-4 \\
\middlehline
Trematomus pennellii & 3.04e-5 & 4.04 & 192 & 0.158 & Demersal & 1.44e-5 & 1.00e-3 \\
\middlehline
Mirounga leonina & 1.20e-4 & 4.87 & 56 & 0.080 & Land-based & 1.41e-5 & 1.28e-3 \\
\middlehline
Notothenia coriiceps & 4.94e-5 & 4.27 & 130 & 0.126 & Demersal & 1.44e-5 & 1.66e-3 \\
\middlehline
Maxilliphimedia longipes & 2.21e-6 & 3.26 & 60 & 0.136 & Benthopelagic & -4.46e-6 & 9.74e-3 \\

\bottomhline
\end{tabular}
\end{table}
```

>>>>

```{=tex}
\begin{table}[t]
\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by interaction strength. References: medianIS = median interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference.}
\begin{tabular}{l c c c c c c}
\tophline

\textbf{Species} & \textbf{medianIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} \\
\middlehline
Mesonychoteuthis hamiltoni & 1.967e-4 & 4.411 & 29 & 0.02781 & Pelagic & 0.02653 \\
\middlehline
Orcinus orca & 1.557e-4 & 5.027 & 26 & 0.03712 & Benthopelagic & 0.02329 \\
\middlehline
Mirounga leonina & 1.314e-4 & 4.868 & 56 & 0.07999 & Land-based & 0.03129 \\
\middlehline
Hydrurga leptonyx & 1.162e-4 & 4.716 & 67 & 0.09429 & Land-based & 0.05824 \\
\middlehline
Leptonychotes weddelli & 1.137e-4 & 4.859 & 59 & 0.08398 & Land-based & 0.02043 \\
\middlehline
Ommatophoca rossii & 1.125e-4 & 4.868 & 56 & 0.07999 & Land-based & 0.02366 \\
\middlehline
Arctocephalus gazella & 1.021e-4 & 4.666 & 61 & 0.09325 & Land-based & 0.03229 \\
\middlehline
Notothenia marmorata & 8.36e-5 & 4.092 & 44 & 0.09066 & Demersal & 0.01840 \\
\middlehline
Macrourus holotrachys & 8.35e-5 & 4.705 & 85 & 0.11151 & Benthopelagic & 0.02399 \\
\middlehline
Macrourus whitsoni & 7.95e-5 & 4.546 & 92 & 0.12373 & Benthopelagic & 0.02235 \\
\middlehline
Balaenoptera acutorostrata & 5.18e-5 & 3.738 & 29 & 0.07843 & Pelagic & -0.02649 \\
\middlehline
Aporocidaris milleri & 2.8e-6 & 3.312 & 60 & 0.07457 & Benthopelagic & -0.02137 \\
\bottomhline
\end{tabular}
\end{table} 
```

### 2023-11-06 Manuscript/SupMaterial.Rmd
Updated Table 1 main manuscript and tables Supp Material

load("QSS_summary_sep22.rda")
knitr::kable(all_data %>% dplyr::select(TrophicSpecies, IS_mean, TotalDegree, TL, meanTrophicSimil) %>% arrange(., desc(IS_mean)), digits = c(0,7,0,2,3), col.names = c("Species","IS_mean", "Degree", "TL", "TS"), caption = "Weighted (interaction strength) and unweighted properties of the species of Weddell Sea food web. Ordered by decreasing mean interaction strength. IS_mean = mean interaction strength, TL = trophic level, TS = trophic similarity.")

@@

We performed extinction simulations, one at a time, for every species in the Weddell Sea food web. In order to assess the impact on the stability of the food web we statistically compared a stability index before and after performing the extinction. For this, we applied Quasi-Sign Stability $QSS$ that calculates the proportion of matrices that are locally stable. These matrices are created by sampling the values of the community matrix (the Jacobian) from a uniform distribution, preserving the sign structure: positive for predators and negative for prey. This stability index was originally proposed by @Allesina2008.
We used the R package multiweb to calculate $QSS$ and to test the $QSS$ difference before and after performing the extinction (Saravia, 2019). Two functions were specifically created for these analyses: ‘calc_QSS’ and ‘calc_QSS_extinction_dif’.
For the $QSS$ calculation we used a uniform distribution between 0 and maximum values given by the parameters negative, positive and self-damping, corresponding to the sign of interactions and self-limitation effect. Since we had estimated the interaction strength for each interaction of the Weddell Sea food web, the limits of the distribution were $negative*-x$,$positive*x$, $self-damping*x$, where $x$ is the value of the strength for the interaction in question.
We performed 1000 extinction simulations for every species. Our results showed that the proportion of Jacobians that were locally stable was zero. Thus, we considered the mean maximum eigenvalue as the stability index, hereafter $QSS$. For testing the $QSS$ difference before and after the extinction we performed an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].

>>>>

load("../Results/QSS_summary_oct31.rda")
knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, IS_median,IS_Q1,IS_Q3, TotalDegree, TL, meanTrophicSimil) %>% arrange(., desc(IS_median)), digits = c(0,7,7,7,0,2,3), col.names = c("Species","median IS","Q1 IS", "Q3 IS", "Degree", "TL", "TS"), caption = "Weighted (interaction strength) and unweighted properties of the species of Weddell Sea food web. Ordered by decreasing mean interaction strength. mean IS = median interaction strength, Q1 IS = First quantil of the IS distribution, Q3 IS = Third quantil of the IS distribution, TL = trophic level, TS = trophic similarity.")

@@

We performed extinction simulations, one at a time, for every species in the Weddell Sea food web. In order to assess the impact on the stability of the food web we statistically compared a stability index before and after performing the extinction. For this, we applied Quasi-Sign Stability $QSS$ that calculates the proportion of matrices that are locally stable. These matrices are created by sampling the values of the community matrix (the Jacobian) from a uniform distribution, preserving the sign structure: positive for predators and negative for prey. This stability index was originally proposed by @Allesina2008.
We used the R package multiweb to calculate $QSS$ and to test the $QSS$ difference before and after performing the extinction (Saravia, 2019). Two functions were specifically created for these analyses: ‘calc_QSS’ and ‘calc_QSS_extinction_dif’.
For the $QSS$ calculation we used a uniform distribution between 0 and maximum values given by the parameters negative, positive and self-damping, corresponding to the sign of interactions and self-limitation effect. Since we had estimated the interaction strength for each interaction of the Weddell Sea food web, the limits of the distribution were $negative*-x$,$positive*x$, $self-damping*x$, where $x$ is the value of the strength for the interaction in question. The $x$ for the self-limitation effect of the species is 0 unless the species present cannibalism.  
We performed 1000 extinction simulations for every species. Our results showed that the proportion of Jacobians that were locally stable was zero, probably due to the absence of self-limitation in the species. Thus, we considered the distribution of maximum eigenvalues as the stability index, hereafter $QSS$. For testing if the $QSS$ difference before and after the extinction is positive or negative we performed performed a contrast. This means that for each simulation we made the difference of the $QSS$ after extinction with the median value of the 1000 simulations of $QSS$ for the complete network, thus we obtained a distribution of $QSS$ differences.
